EvoSuite at the SBST 2016 Tool Competition

### 2016-02-16 papers/sbst16/paper_sbst16.tex
draft for SBST 16 competition

\hypersetup{
colorlinks=true,
urlcolor=rltblue,
linkcolor=rltred,
citecolor=rltgreen,
bookmarksnumbered=true,
pdftitle={EvoSuite at the SBST 2013 Tool Competition},
pdfauthor={Gordon Fraser and Andrea Arcuri},
pdfsubject={Test case generation},
pdfkeywords={Test case generation, unit testing, test
  oracles, assertions, search based testing}
}

@@

%\title{Unit Testing Tool competition: Results for EvoSuite}
\title{EvoSuite at the SBST 2015 Tool Competition}

@@

\begin{abstract}
  \EVOSUITE is a mature research prototype that automatically
  generates unit tests for Java code.  This paper summarizes the
  results and experiences of \EVOSUITE's participation at the third
  unit testing competition at SBST 2015. An unfortunate issue of
  conflicting dependency versions in two out of the nine benchmark
  projects reduced \EVOSUITE's overall score to $190.6$, leading to
  the overall second rank.
\end{abstract}

@@

This paper describes the results of applying the \EVOSUITE test
generation tool~\cite{FrA11c} to the benchmark used in the tool
competition at the International Workshop on Search-Based Software
Testing (SBST) 2015.  Details about the competition and the benchmark
can be found in~\cite{sbst2015}. In this competition, \EVOSUITE ranked
second with a score of $190.6$.

@@

  \hline
  \multicolumn{2}{|l|}{Operation} \\
  \hline
  Interaction &  Through the command line, and Eclipse plugin\\
  User guidance &  manual verification of assertions for functional faults\\
  Source of information &  http://www.evosuite.org \\
  Maturity&  Mature research prototype, under development\\
  Technology behind the tool & Search-based testing / whole test suite generation\\
\hline
  \multicolumn{2}{|l|}{Obtaining the tool and information} \\
  \hline
License & GNU General Public License V3\\
Cost & Open source\\
Support & None \\
\hline
\hline
  \multicolumn{2}{|l|}{Does there exist empirical evidence about} \\
  \hline
  Effectiveness and Scalability & See~\cite{GoA_TSE12,fraser2014large}. \\
%Completeness & \\
%Effectiveness & \\
%Efficiency & \\
%Defect types & \\
%Scalability & \\
%Comprehensibility & \\
%Learnability & \\
%Subjective satisfaction & \\
%Other & \\
\hline
\end{tabular}\vspace{-1em}
\end{table}

\EVOSUITE~\cite{FrA11c,GoA_TSE12} automatically generates test suites
for Java classes, targeting branch coverage and other coverage
criteria (e.g., mutation testing~\cite{emse14_mutation}). \EVOSUITE
works at the Java bytecode level, i.e., it does not require source
code. It is fully automated and requires no manually written test
drivers or parameterized unit tests.  For example, when \EVOSUITE is
used from its Eclipse plugin, a user
just needs to select a class, and tests are generated with a mouse-click.

\EVOSUITE has been evaluated on millions of lines of Java
code~\cite{fraser2014large}, both open-source code and close-source
code provided by one of our industrial partners.  In the previous two
editions of the unit testing tool competition, \EVOSUITE ranked
first~\cite{evosuiteAtSbst2013,evosuiteAtFittest2013}.

\EVOSUITE uses an evolutionary approach to derive these test suites: A
genetic algorithm evolves candidate individuals (chromosomes) using
operators inspired by natural evolution (e.g., selection, crossover
and mutation), such that iteratively better solutions with respect to
the optimization target (e.g., branch coverage) are produced.  For
details on this test generation approach we refer to~\cite{GoA_TSE12}.
To improve performance further, we are investigating several
extensions to \EVOSUITE. 
For example, \EVOSUITE can employ dynamic
symbolic execution~\cite{evoISSRE113} 
and memetic algorithms~\cite{fraser2014memetic}
to handle the cases in which our genetic algorithm may struggle.

@@

We configured \EVOSUITE to use a dynamic timeout of maximum 10 minutes
per class for the search, with an earlier stop if the fitness value
did not increase for two minutes. The fitness function to drive the
genetic algorithm was based on a combination of line coverage, branch
coverage, and weak mutation testing~\cite{emse14_mutation}. We enabled
the post-processing step of test minimization, but to reduce the time
spent we included all assertions rather than filtering them with
mutation analysis~\cite{10.1109/TSE.2011.93}. In practice, this may
not result in the most readable or maintainable test cases, but
neither of these two attributes is measured by the SBST contest
metric.

@@

\begin{table*}[t]
  \centering
  \caption{\label{table:results}Detailed results of \EVOSUITE on the SBST benchmark classes. Time is expressed in minutes.}
  %\scriptsize
\resizebox{0.9\textwidth}{!}{  
  \begin{tabular}{l rrrrrr} \toprule
Class &  JUnit Files &   Generation Time & Execution Time   & \% Line Coverage & \% Branch Coverage & \% Mutation Score \\  
% Class & Generation Time & Execution Time  & Tests & Line Coverage & Branch Coverage & Mutation Score \\ 
%Class & \multicolumn{2}{c}{ Time} & Tests & Line Coverage & Branch
%Coverage & Mutation Score \\ 
%& Generation & Execution & & & & \\
\midrule
\input{results.tex}
\midrule
Average & & 6.19 & 0.03 & 55.36 & 47.19 & 41.02\\
\bottomrule
  \end{tabular}
}
\end{table*}

%average per class generation time:                 371.581857 seconds
%average per class execution time:                  2.103966 seconds
%average per class instruction coverage:            54.495767 %
%average per class line coverage:                   55.368111 %
%average per class branch coverage:                 47.192896 %
%average per class method coverage:                 59.628209 %
%average per class mutation coverage:               41.024248 %

The results of \EVOSUITE on the benchmark classes are listed in
Table~\ref{table:results}. On average, \EVOSUITE achieved 55.36\% line
coverage, 47.19\% branch coverage\footnote{Using Cobertura's definition
  of branch coverage, which only counts conditional statements, not
  edges in the CFG.}, and 41.02\% mutation score. 
%On average, \EVOSUITE
%produced TODO tests per class, and it took an average of TODO per class to
%do so.
% (with \EVOSUITE configured to 3 minutes per class).
On average, \EVOSUITE took 6 minutes and 11 seconds per class to generate test cases. 
The generated test suites take on average 2.1 seconds to run per class.

@@

% CharMatcher: Timeout
% CycleHandler, WikipediaInfo: Infinite loop in generic resolving
% Response requires java.net.HttpURLConnection

Out of 63 classes under test (CUTs), \EVOSUITE did not manage to
obtain any coverage for 18, i.e., 28\% of all classes.  For 14 of them
(seven in the twitter4j project and seven in the hibernate project),
this is due to a mismatch in libraries on the classpath.  In
particular, \EVOSUITE does bytecode instrumentation using the ASM
library (currently using version 5.0.3).  However, the projects of the
CUTs had their own (older) version of ASM; for example Twitter4J has
an indirect dependency to ASM 3.2.

Because the API of ASM has changed over different versions, this leads
to errors like: ``java.lang.IncompatibleClassChangeError: class
org.objectweb.asm.tree.ClassNode has interface
org.objectweb.asm.ClassVisitor as super class''.  Note: \EVOSUITE can
be applied to its own library dependencies through its use of
customized classloaders. However, bytecode instrumentation is also
performed in the generated JUnit files (e.g., to support environment
testing based on mock objects~\cite{arcuri2014automated}), which leads
to a runtime dependency to ASM. Consequently, \EVOSUITE generates
tests for those 14 classes, but then all these tests fail due to the
above mentioned exception.  An easy solution would be to ship
\EVOSUITE with its own ASM version using a different package name
(e.g., by using the JarJar
tool\footnote{https://code.google.com/p/jarjar/}).
%
If we had handled this issue properly before the competition, this
would have changed the outcome: Excluding classes from the twitter4j
and hibernate, the overall score of \EVOSUITE would be 191.584,
whereas the first ranked tool (GRT) would have a score of
164.464. Consequently, this issue clearly is the main factor affecting
\EVOSUITE's overall result.

For the other four classes with 0\% coverage, \EVOSUITE failed to
generate any tests for other reasons. For \<CharMatcher>, there was 
an issue in how \EVOSUITE handled timeouts, which resulted in
\EVOSUITE's master process killing the client process before tests
were written to disk. For \<CycleHandler> and \<WikipediaInfo>,
\EVOSUITE ran into an issue when trying to resolve the generic type
parameters of some dependency classes; this also affects \<Page> with
1.49\% coverage. This issue could be avoided by omitting generic type
parameters, as the Java compiler would only issue warnings about such
missing parameters. However, as \EVOSUITE is aiming to produce
readable tests, we feel it is important to properly handle Java
Generics. Finally, for \<Response> the constructor requires a
parameter of type \<java.net.HttpURLConnection>, which is an abstract
class without concrete subclasses. As \EVOSUITE does not produce stubs
automatically, it therefore failed to instantiate \<Response> objects.

%There are also a further 4 cases of low coverage (e.g., less than
%30\%).  For example, if look at line coverage, then we have \<Page>
%with 1.49\%, \<AbstractInstance> with 13.28\%,
%\<CategoryDescendantsIterator> with 8.24\% and \<PageQueryIterable>
%with 18.57\%.

%TODO: Will look into these four.

%To improve \EVOSUITE, it will be important to
%understand why that was the case.

@@

With an overall score of $190.6$, \EVOSUITE achieved the second
highest score of all tools in the competition. The score calculated
for the best tool is $203.7$: a very close call.  In particular, if
considering only projects without a configuration issue in the
classpath of the target projects, \EVOSUITE would have scored first
with a score of $191.6$.
%
%due to
%a configuration issue in the classpath of the target projects,
%\EVOSUITE could had been run only on 7 out of 9 of the projects used
%as benchmark.  
The underlying issue can be easily fixed for future runs of the
competition.
% issue that would lead to even
%higher scores.

@@

%\noindent
%\textbf{Acknowledgments.}

>>>>

\hypersetup{
colorlinks=true,
urlcolor=rltblue,
linkcolor=rltred,
citecolor=rltgreen,
bookmarksnumbered=true,
pdftitle={EvoSuite at the SBST 2016 Tool Competition},
pdfauthor={Gordon Fraser and Andrea Arcuri},
pdfsubject={Test case generation},
pdfkeywords={Test case generation, unit testing, test
  oracles, assertions, search based testing}
}

@@

%\title{Unit Testing Tool competition: Results for EvoSuite}
\title{EvoSuite at the SBST 2016 Tool Competition}

@@

\begin{abstract}
  \EVOSUITE is a search-based tool that automatically
  generates unit tests for Java code.  This paper summarizes the
  results and experiences of \EVOSUITE's participation at the fourth
  unit testing competition at SBST 2016. 
\end{abstract}

@@

This paper describes the results of applying the \EVOSUITE test
generation tool~\cite{FrA11c} to the benchmark used in the tool
competition at the International Workshop on Search-Based Software
Testing (SBST) 2016.  Details about the competition and the benchmark
can be found in []. 
In this competition, \EVOSUITE ranked [] with a score of [].

@@

  \hline
  \multicolumn{2}{|l|}{Operation} \\
  \hline
  Interaction &  Through the command line, and plugins for IntelliJ, Maven and Eclipse\\
  User guidance &  manual verification of assertions for functional faults\\
  Source of information &  http://www.evosuite.org \\
  Maturity&  Mature research prototype, under development\\
  Technology behind the tool & Search-based testing / whole test suite generation\\
\hline
  \multicolumn{2}{|l|}{Obtaining the tool and information} \\
  \hline
License & Lesser GPL V.3\\
Cost & Open source\\
Support & None \\
\hline
\hline
  \multicolumn{2}{|l|}{Does there exist empirical evidence about} \\
  \hline
  Effectiveness and Scalability & See~\cite{GoA_TSE12,fraser2014large}. \\
%Completeness & \\
%Effectiveness & \\
%Efficiency & \\
%Defect types & \\
%Scalability & \\
%Comprehensibility & \\
%Learnability & \\
%Subjective satisfaction & \\
%Other & \\
\hline
\end{tabular}\vspace{-1em}
\end{table}

\EVOSUITE~\cite{FrA11c,GoA_TSE12} automatically generates test suites
for Java classes, targeting branch coverage and other coverage
criteria (e.g., mutation testing~\cite{emse14_mutation}). \EVOSUITE
works at the Java bytecode level, i.e., it does not require source
code. It is fully automated and requires no manually written test
drivers or parameterized unit tests.  For example, when \EVOSUITE is
used from its Eclipse and IntelliJ plugins, a user
just needs to select a class, and tests are generated with a mouse-click.

\EVOSUITE has been evaluated on millions of lines of Java
code~\cite{fraser2014large}, both open-source code and close-source
code provided by one of our industrial partners.  In the first two
editions of the unit testing tool competition, \EVOSUITE ranked
first~\cite{evosuiteAtSbst2013,evosuiteAtFittest2013}, whereas it
ranked second in the third one [].

\EVOSUITE uses an evolutionary approach to derive these test suites: A
genetic algorithm evolves candidate individuals (chromosomes) using
operators inspired by natural evolution (e.g., selection, crossover
and mutation), such that iteratively better solutions with respect to
the optimization target (e.g., branch coverage) are produced.  For
details on this test generation approach we refer to~\cite{GoA_TSE12}.
%To improve performance further, we are investigating several
%extensions to \EVOSUITE. 
%For example, \EVOSUITE can employ dynamic
%symbolic execution~\cite{evoISSRE113} 
%and memetic algorithms~\cite{fraser2014memetic}
%to handle the cases in which our genetic algorithm may struggle.

@@

%We configured \EVOSUITE to use a dynamic timeout of maximum 10 minutes
%per class for the search, with an earlier stop if the fitness value
%did not increase for two minutes. The fitness function to drive the
%genetic algorithm was based on a combination of line coverage, branch
%coverage, and weak mutation testing~\cite{emse14_mutation}. We enabled
%the post-processing step of test minimization, but to reduce the time
%spent we included all assertions rather than filtering them with
%mutation analysis~\cite{10.1109/TSE.2011.93}. In practice, this may
%not result in the most readable or maintainable test cases, but
%neither of these two attributes is measured by the SBST contest
%metric.

@@

\begin{table*}[t]
  \centering
  \caption{\label{table:results}Detailed results of \EVOSUITE on the SBST benchmark classes. Time is expressed in minutes.}
  %\scriptsize
\resizebox{0.9\textwidth}{!}{  
  \begin{tabular}{l rrrrrr} \toprule
Class &  JUnit Files &   Generation Time & Execution Time   & \% Line Coverage & \% Branch Coverage & \% Mutation Score \\  
\midrule
%\input{results.tex}
\midrule
%Average & & 6.19 & 0.03 & 55.36 & 47.19 & 41.02\\
\bottomrule
  \end{tabular}
}
\end{table*}

The results of \EVOSUITE on the benchmark classes are listed in
Table~\ref{table:results}. On average, \EVOSUITE achieved []\% line
coverage, []\% branch coverage\footnote{Using Cobertura's definition
  of branch coverage, which only counts conditional statements, not
  edges in the CFG.}, and []\% mutation score.

@@

[]

@@

With an overall score of [], \EVOSUITE achieved the []
 score of all tools in the competition.

@@

%\noindent
\textbf{Acknowledgments.}
